NGO analysis

### 2022-08-03 Dashboard/NGO Analysis dashboard v006.Rmd
Adding links.

---
title: "NGO analysis"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    theme: lumen
runtime: shiny
---

@@

Then upload an Excel file in the set format. <!--# Need to insert link when repository is public -->

>>>>

---
title: "NGO analysis"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    theme: lumen
    source_code: https://github.com/torbjornso/ISSSV1337group5
runtime: shiny
---

@@

Then upload an Excel file in the [set format](https://github.com/torbjornso/ISSSV1337group5/blob/27d1d4c25882091d6aef51956000f7ef3fefff75/Dashboard/Data/NGO_template.xltx).
